Analysis v1.2 mash

### 2023-09-08 R/Analysis_v1.2_mash_using_greedy_covar.Rmd
analysis: run mash using covar mat from greedy mash algorithm

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(bigsnpr)
library(switchgrassGWAS)
library(mashr)
library(rlist)
library(cowplot)
library(here)
library(zoo)
```

@@

#

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(bigsnpr)
library(mashr)
library(switchgrassGWAS)
library(rlist)
library(cowplot)
library(here)
library(zoo)
```

@@

For mashr: Sometimes install.packages("RcppGSL") is also needed.
#
